An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-06-03 tex/response.tex

\section{Major comments}

\begin{itemize}
\item \textit{suggested title change}: This has been changed to ``An open
    framework for the reproducible study of the iterated prisoner's dilemma''
\item \textit{Implementation \& Architecture section currently discusses how to
    use library, but should be refactored to expand upon architecture}: The
    various examples have been moved to the Reuse section and an extra paragraph
    explaining the structure has been added.
\item \textit{Side-by-side figures appear too small, and should be replaced with
    full-size (perhaps top-bottom) figures}: Figures have been resized.
\item \textit{Discrepancy between version of software in paper and on Zenodo}:
    This has been addressed.
\item \textit{Dependencies not automatically installed or checked via pip}: This
    has been addressed. Here is a url to the code patch (github pull request)
    that fixed this: \url{https://github.com/Axelrod-Python/Axelrod/pull/542}.
\end{itemize}

\section{Minor comments}

We have addressed almost all of the minor comments, these can be viewed in
detail here:
\url{https://github.com/Axelrod-Python/An-open-reproducible-framework-for-the-study-of-the-iterated-prisoners-dilemma/compare/jors...jors-r1-vk}.

### 2016-06-07 tex/paper.tex
Comments from Marc.

As stated in the \textbf{Introduction}, one of the main goals of the library is
to allow for the easy contribution of strategies. Doing this requires the
writing of a simple Python class (which can inherit from other predefined
classes). All components of the library are automatically tested using a
combination of unit, property and integration tests, these tests are run as new
features are added to the library to ensure compatibility (they are also run
automatically using \url{travis-ci.org}). Thus, when submitting a strategy, a
simple test is required which ensures the strategy behaves as expected.  Full
contribution guidelines can be found in the documentation, which is also part of
the library itself and is hosted using \url{readthedocs.org}.  As an example,
Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as its corresponding test.

@@

You can see an overview of the structure of the source code in
Figure~\ref{fig:overview}. This shows the parallel collection of strategies and
their tests. Furthermore the underlying engine for the library is a class for
tournaments which lives in the \texttt{tournament.py} module. This class is
responsible for coordinating the play of generated matches (from the
\texttt{match.py} module). This generation of matches is the responsibility of a
match generator class (in the \texttt{match\_generator.py} module) which is
designed in such a way as to be easily modifiable to create new types of
tournaments. This is described fuller in a tutorial in the documentation which
shows how to easily create a tournament where players only play each other with
probability 0.5.  This will be discussed further in the reuse section of this
paper.

@@

To date the library has had contributions from 25 contributors from a variety
of backgrounds which are not solely academic. These contributions have been in
terms of strategies. One strategy is the creation of an undergraduate
mathematics student with little prior knowledge of programming. Multiple other
strategies were written by a 15 year old secondary school student. Both of
these students are authors of this paper. As well as these strategy
contributions, vital architectural improvements to the library itself have also
been received.

@@

The library is continuously tested for compatibility with Python 2.7, 3.4 and 3.5.

@@

\begin{multicols}{2}
    \begin{itemize}[noitemsep,topsep=0pt]
        \item Numpy 1.9.2
        \item Matplotlib 1.4.2
        \item Testfixtures 4.9.1
        \item Hypothesis 3.0 (only a requirement for development)
    \end{itemize}
\end{multicols}

@@

The Axelrod library has been designed with sustainable software practice in
mind. There is an extensive documentation suite:
\url{axelrod.readthedocs.org/en/latest/}. Furthermore, there is a growing set
of example Jupyter notebooks available here:
\url{https://github.com/Axelrod-Python/Axelrod-notebooks}.

The ability to have readily available a large number of strategies makes this
tool an excellent and obvious example of the benefits of open research which
should positively impact the game theoretic community.
This has been evidenced by the work described: the library has already shown
its potential for reuse.

Installation of the library is straightforward as it is available via the
standard Python installation package: `pip'
(\url{https://pypi.python.org/pypi}). The package name is \texttt{axelrod} and
can thus be installed by calling: \texttt{pip install axelrod}. This ensures it
can be used on all major operating systems (Windows, OS X and Linux).

@@

Despite this, due to previous research being done in an irreproducible manner
with, for example, no source code and/or vaguely described strategies, not all
previous tournaments can yet be reproduced. In fact, some of the early
tournaments might be impossible to reproduce as the source code is forever
lost. This library aims to prevent this from happening again in the future.

@@

This can be reproduced as shown in Figure~\ref{fig:stewart-code}, which gives
the plot of Figure~\ref{fig:stewart_tournament}. Note that slight differences
with the results of \cite{Stewart2012} are due to stochastic behaviour.

@@

In parallel to the Python library, a tournament is being kept up to date that
pits all available strategies against each other. Figure~\ref{fig:tournament}
shows the results from the full tournament which can also be seen (in full
detail) here: \url{http://axelrod-tournament.readthedocs.org/}. Data sets are
also available showing the plays of every match that takes place. Note that to
obtain this tournament requires a simple change of the code shown in
Figure~\ref{fig:demo_tournament_commands}, changing:

@@

The current winning strategy is a novel strategy: Looker Up. This is a
strategy that maps a given set of states to actions. The state space is defined
generically by \(m, n\) so as to map states to actions as shown
in~(\ref{equ:example_of_lookerup}).

>>>>

As stated in the \textbf{Introduction}, one of the main goals of the library is
to allow for the easy contribution of strategies. Doing this requires the
writing of a simple Python class (which can inherit from other predefined
classes). All components of the library are automatically tested using a
combination of unit, property and integration tests. These tests are run as new
features are added to the library to ensure compatibility (they are also run
automatically using \url{travis-ci.org}). When submitting a strategy, a
simple test is required which ensures the strategy behaves as expected.  Full
contribution guidelines can be found in the documentation, which is also part of
the library itself and is hosted using \url{readthedocs.org}.  As an example,
Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as its corresponding test.

@@

You can see an overview of the structure of the source code in
Figure~\ref{fig:overview}. This shows the parallel collection of strategies and
their tests. Furthermore the underlying engine for the library is a class for
tournaments which lives in the \texttt{tournament.py} module. This class is
responsible for coordinating the play of generated matches (from the
\texttt{match.py} module). This generation of matches is the responsibility of a
\textit{match generator} class (in the \texttt{match\_generator.py} module)
which is designed in such a way as to be easily modifiable to create new types
of tournaments. This is described further in a tutorial in the documentation
which shows how to easily create a tournament where players only play each other
with probability 0.5.  This will be discussed further in the reuse section of
this paper.

@@

To date the library has had contributions from 25 contributors from a variety of
backgrounds which are not solely academic. These contributions have been mostly
in terms of strategies. One strategy is the creation of an undergraduate
mathematics student with little prior knowledge of programming. Multiple other
strategies were written by a 15 year old secondary school student. Both of these
students are authors of this paper. As well as these strategy contributions,
vital architectural improvements to the library itself have also been
contributed.

@@

The library is continuously tested for compatibility with Python 2.7 and the two
most recent python 3 releases.

@@

\begin{multicols}{2}
    \begin{itemize}[noitemsep,topsep=0pt]
        \item Numpy 1.9.2
        \item Matplotlib 1.4.2 (only a requirement if graphical output is
            required)
        \item Tqdm 3.4.0
        \item Hypothesis 3.0 (only a requirement for development)
    \end{itemize}
\end{multicols}

@@

The Axelrod library has been designed with sustainable software practices in
mind. There is an extensive documentation suite:
\url{axelrod.readthedocs.org/en/latest/}. Furthermore, there is a growing set
of example Jupyter notebooks available here:
\url{https://github.com/Axelrod-Python/Axelrod-notebooks}.

The availability of a large number of strategies makes this
tool an excellent and obvious example of the benefits of open research which
should positively impact the game theory community.
This is evidently true already as the library has been used to study and create
interesting and powerful new strategies.

Installation of the library is straightforward via standard python installation
repositories (\url{https://pypi.python.org/pypi}). The package name is
\texttt{axelrod} and can thus be installed by calling: \texttt{pip install
axelrod} on all major operating systems (Windows, OS X and Linux).

@@

Nevertheless, due to previous research being done in an irreproducible manner
with, for example, no source code and/or vaguely described strategies, not all
previous tournaments can yet be reproduced. In fact, some of the early
tournaments might be impossible to reproduce as the source code is apparently
forever lost. This library aims ensure reproducibility in the future.

@@

This can be reproduced as shown in Figure~\ref{fig:stewart-code}, which gives
the plot of Figure~\ref{fig:stewart_tournament}. Note that slight differences
with the results of \cite{Stewart2012} are due to stochastic behaviour of some
strategies.

@@

In parallel to the Python library, a tournament is being kept up to date that
pits all available strategies against each other. Figure~\ref{fig:tournament}
shows the results from the full tournament which can also be seen (in full
detail) here: \url{http://axelrod-tournament.readthedocs.org/}. Data sets are
also available showing the plays of every match that takes place. Note that to
recreate this tournament simply requires changing a single line of the code
shown in Figure~\ref{fig:demo_tournament_commands}, changing:

@@

The current winning strategy is new to the research literature: Looker Up. This
is a strategy that maps a given set of states to actions. The state space is
defined generically by \(m, n\) so as to map states to actions as shown
in~(\ref{equ:example_of_lookerup}).
